Using Nature Inspired Algorithms for Feature Selection in Transaction Fraud Detection

### 2020-05-31 paper/main.tex
Fix alignment of the document

When comparing the population sizes, all of the algorithms achieved the best results when the population size was highest (50). The only exception is Cuckoo Search, which found the most optimal solution with population size of 10, however the difference negligible. Table \ref{tab:nia_comparison}. shows the algorithm scores for each population. Figure \ref{fig:nia_train_score_by_algorithm_1}. \& \ref{fig:nia_train_score_by_algorithm_2}.shows the differences in scores between population size of 10 and 50.

@@

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired algorithms for population size of 10.}
    \label{fig:nia_train_score_by_algorithm_1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired algorithms for population size of 50.}
    \label{fig:nia_train_score_by_algorithm_2}
\end{figure}

@@

\begin{figure}[ht]
	\begin{center}
	    \includegraphics[width=10cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}

@@

In our experiments, we found out Grey Wolf Optimizer as the best nature-inspired algorithm for feature selection. It achieved significantly better results than other nature-inspired algorithms and better results that recursive feature elimination.

GWO alongside Bat Algorithm was the only nature-inspired algorithms that were able to converge during the optimization process. We assume that other algorithms might converge too if we experimented with their parameter settings. We consider the fact, that GWO does not have any parameters other than population size as a big strength, because it saves a significant amount of optimization time.

@@

% TODO: concusion in the topic of transaction fraud detection

>>>>

When comparing the population sizes, all of the algorithms achieved the best results when the population size was highest (50). The only exception is Cuckoo Search, which found the most optimal solution with population size of 10, however the difference negligible. Table \ref{tab:nia_comparison}. shows the algorithm scores for each population. Figure \ref{fig:nia_train_score_by_algorithm_1}. \& \ref{fig:nia_train_score_by_algorithm_2}. shows the differences in scores between population size of 10 and 50.

@@

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired in 5 runs algorithms for population size of 10.}
    \label{fig:nia_train_score_by_algorithm_1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired algorithms in 5 runs for population size of 50.}
    \label{fig:nia_train_score_by_algorithm_2}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
	    \includegraphics[width=10cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm in 5 runs - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}

\newpage

@@

In our experiments, we found out Grey Wolf Optimizer as the best nature-inspired algorithm for feature selection. It achieved significantly better results than other nature-inspired algorithms. Grey Wolf Optimizer achieved even better results than recursive feature elimination (+1.4\% ROC AUC), while using by half fewer features.

Grey Wolf Optimizer alongside Bat Algorithm was the only nature-inspired algorithms that were able to converge during the optimization process. We assume that other algorithms might converge too if we experimented with their parameter settings. We consider the fact, that GWO does not have any parameters other than population size as a big strength, because it saves a significant amount of optimization time.

@@
